Cover Times of Random Walks

### 2019-04-23 paper.tex
matthews lower on binary

\abstract{abstract}

@@

"white screen" problem
numerous applications
many mathematical tools

\subsection{Motivation}
universal travel sequences
graph connectivity
protocol testing

@@

@@

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\tcov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
\end{align}

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i)/(n-1)$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (ln-1)(n-i)$.
Then
\begin{align}
\tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

A natural interpretation of the cover time on a complete graph is 
the so-called coupon collecting problem.
There are $r$ different coupons that are randomly packaged in cereal boxes.
An avid fan buys a box of cereal every day.
We want to know how many days until the fan has collected each coupon.
The strategy is to think of every coupon as a vertex on the complete graph.
We then move from vertex to vertex with uniform probability.
The difference between the coupon collecting problem and the complete graph
is that we now have self-edges.
Before, we had to leave our current vertex at each step.
Now, we can stay in the same vertex (provided our collector found the same coupon
two days in a row).
We apply our approach to the complete graph and substitute the $r$ possible coupons
we can find for the $n-1$ vertices we could move to.
Then
\begin{align}
\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
\end{align}

@@

\begin{align}
\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

@@

\begin{align}
(e_i - e_1) &= (i-1) e_1 - 2[1+2+...+i-1] \nonumber \\
e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
&= i(N-1 - i + 1) = i(N-i)
\label{eq:line}
\end{align}

@@

We write
\begin{align}
\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + ... + \E_{i}[T_{i+1}] + ... + \E_{N-1}[T_N]. \nonumber
\end{align}

@@

Then
\begin{align}
\E_0[T_N] &= 1 + 3 + ... + 2i - 1 + ... + 2(N-1) -1 \nonumber \\
&= N^2 \nonumber
\end{align}

@@

\begin{theorem}[Matthews Upper Bound]
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_up}
\end{theorem}
\begin{align}
\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
\end{align}

\begin{proof}
Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
We may assume that the walk started at vertex $n$.
Let $\sigma$ be a uniform permutation of the unvisited $n-1$ vertices.
The strategy is to look for the vertices in order $\sigma$.

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited the first
time they are all visited.

We begin by writing the cover time in a clever way
(similar to the strategy we employed on the cycle graph):
\begin{align}
\tcov &= \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + ... + 
(T_k - T_{k-1}) + ... + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

Putting it all together,
\begin{align}
\tcov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
+ ... + \frac{1}{n-1} \right). \nonumber
\end{align}
\end{proof}

@@

\begin{theorem}[Matthews Lower Bound]
Let $A \subseteq V(G)$. Define $\tmina = \min_{a,b\in A, a \neq b} \E_b[T_a]$.
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_low}
\end{theorem}
\begin{align}
\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + ... +
\frac{1}{|A| -1} \right). \nonumber
\end{align}

\begin{proof}
Without loss of generality, label the vertices $\{1, 2, ..., n\}$.
We may assume that the walk started at vertex $x \in A$.
Let $\sigma$ be a uniform permutation of the vertices in $A$.
The strategy is to look for the vertices in order $\sigma$.

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$.

We again write the cover time in a clever way:
\begin{align}
\tcov &\geq \E_x[T_1 + (T_2 - T_1) + ... + 
(T_k - T_{k-1}) + ... + (T_{|A|} - T_{|A|-1})] . \nonumber
\end{align}

@@

Putting it all together,
\begin{align}
\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + ... + \frac{1}{k} 
+ ... + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
&= \tmina \left( 1 + \frac{1}{2} + ... + \frac{1}{k} 
+ ... + \frac{1}{|A|-1} \right). \nonumber
\end{align}
\end{proof}

@@

\cite{LP17}
Consider an unweighted binary tree as in \cref{fig:binary} with a single root $\rho$.
A vertex has two children if it is distance less than $k$
from the root and no children if it is a leaf (distance $k$ from the root).
There are $n = 1 + 2 + 4 + ... + 2^k = 2^{k+1} - 1$ vertices.

By \cref{eqn:commute}, the commute time between the root and a leaf $a$ is
\begin{align}
C R_{\rho, a} = 2 (n-1) k \nonumber
\end{align}
Note that the resistance adds in series so $\Rxy = i$ where $i$
is the length of the single path between $x$ and $y$.

The maximum hitting distance is between two vertices whose 
mose recent common ancestor is the root.
For this pair, the hitting time is the same as the commute time
to the root by symmetry.
Consider $a$ and $b$ two leaves whose most recent common ancestor
is the root.
Then
\begin{align}
\E_a [T_b] = \E_a [T_\rho] + \E_\rho [T_a] = 2 (n-1) k \nonumber
\end{align}

and \cref{thm:matthews_up} gives
\begin{align}
\tcov \leq 2(n-1)k\left(1 + \frac{1}{2} + ... + \frac{1}{n} \right). \nonumber
\end{align}

\todo{add lower bound}

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale = 2]
	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .25pt,-,black!100]
	    \tikzstyle{span}=[draw,line width = 2pt,-,black!100]
	    \node[vertex] (0) at (0,0) {};
	    \node[vertex] (1) at (1,0) {};
	    \node[vertex] (2) at (1,1) {};
	    \node[vertex] (3) at (0,1) {};
	    \draw[span] (0) -- (1);
	    \draw[edge] (0) -- (2);
	    \draw[edge] (0) -- (3);
	    \draw[span] (1) -- (2);
	    \draw[edge] (1) -- (3);
	    \draw[span] (2) -- (3);
	\end{tikzpicture}
	\caption{A spanning tree of the complete graph with $n=4$.}\label{fig:span}
\end{figure}

@@

\begin{proof}
Given a spanning tree $\T$, there exists a vertex $v$ with only one edge.
Consider the path $v_0, v_1, ..., v_{2n-2}$ where $v=v_0=v_{2n-2}$
that traverses each edge in the spanning once in each direction
and covers every vertex.
We construct this path by starting at $v$ and walking along all $n-1$ edges to the
other vertex with only one edge and then coming back to $v$.

@@

\section{Distributional Aspects}
\cite{Du11}
We consider the distribution of the cover time of a random walk
on the complete graph with self edges.
Call $r$ the number of steps since we began the random walk.
Let $A_i$ be the event that vertex $i$ is not visited and
$N_n$ the number of unvisited vertices.
Then
\begin{align}
P(A_i) = (1-1/n)^r \nonumber
\end{align}
and
\begin{align}
\E[N_n] = n(1-1/n)^r. \nonumber
\end{align}

@@

As $n \rightarrow \infty$,
\begin{align}
\Var(N_n/n) &= \Var(N_n) / n^2 \nonumber\\
&\rightarrow (1-2/n)^r - (1-1/n)^{2r} = e^{-2c} - (e^{-c})^2 = 0. \nonumber
\end{align}

@@

We prove the following theorem and then use it to show that $\cov \sim \textrm{Pois}(e^{-x})$.
\begin{theorem}\label{thm:pois}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}

@@

By the principle of inclusion-exclusion,
\begin{align}
p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + ... \nonumber\\
&= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \nonumber
\end{align}

@@

Our strategy is to show that $p_m(r,n) \rightarrow \frac{\lambda^m}{m!}e^{-\lambda}$.
The first step is to prove that
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r \rightarrow \lambda ^m /m! \nonumber
\end{align}

We bound the expression from the top and the bottom and use the dominated convergence
theorem.
We will first show the upper bound.
Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
$ne^{r/n} \rightarrow \lambda$.
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} \nonumber \\
&= \frac{(n e^{r/n})^m} {m!} \nonumber \\
&\rightarrow \frac{\lambda ^m} {m!} \nonumber
\end{align}

We now turn to the more tricky lower bound.
Notice that ${n \choose m} \geq (n-m)^m / m!$
\todo{why?}
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r &\geq \left(1-\frac{m}{n}\right)^r (n-m)^m / m! \nonumber\\
&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  / m! \nonumber
\end{align}

As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$
and $1/m!$ is constant.
We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
to bound the rest of the term.
Notice that
\begin{align}
\log(1-t) &= 0 - t - t^2/2 -t^3/3 - ... \nonumber\\
&\geq -t -t^2/2(1 + 1/2 + 1/4 + ...) = -t - t^2 \nonumber
\end{align}
and so we have
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
& \geq m \log n - r m /n - r m/n^2. \nonumber
\end{align}

\todo{why?}
Our assumption that $ne^{r/n} \rightarrow \lambda$ implies that
\begin{align}
r = n \log n - n \log \lambda + o(n) \nonumber
\end{align}
so $r(m/n)^2 \rightarrow 0$.
Then
\begin{align}
rm/n &=m \log n - m \log \lambda + o(n)m/n \nonumber
\end{align}
and in particular
\begin{align}
m \log \lambda &\rightarrow m \log n - rm/n \nonumber
\end{align}
so
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&\geq m \log n - rm/n. \nonumber
\end{align}
It follows that
\begin{align}
\lim_{n\rightarrow \infty} n^m\left(1-\frac{m}{n}\right)^r
&\geq \lambda^m. \nonumber
\end{align}

Now we put together the pieces.
To begin,
\begin{align}
{ n \choose m } (1-\frac{m}{n})^r \rightarrow \lambda^m /m! \nonumber
\end{align}
so
\begin{align}
p_0(r,n) \rightarrow \sum_{k=0}^\infty \lambda^k /k! = e^{-\lambda}. \nonumber
\end{align}

The result holds for
\begin{align}
p_0(r,n-m) \rightarrow e^{-\lambda} \nonumber
\end{align}
since $m$ is fixed and $(n-m)e^{r/(n-m)} \rightarrow \lambda$.

Finally,
\begin{align}
p_m(r,n) &= {n \choose m} (1-\frac{m}{n})^r p_0(r, n-m) \nonumber \\
&\rightarrow \frac{\lambda^m}{ m!} e^{-\lambda} \nonumber
\end{align}
so we have that $N_n \rightarrow \textrm{Pois}(\lambda)$ as claimed.

@@

Set $r = n \log n + nx$.
Then 
\begin{align}
ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
&= n e {- \log n} e^ {- x} = e^{-x}.\nonumber
\end{align}

Consider the cover time variable $\cov$.
Since $\cov \leq m$ if and only if the first $m$ steps
of the random walk visit all $n$ vertices, then by \cref{thm:pois},
\begin{align}
\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber
\end{align}
and
\begin{align}
\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \nonumber
\end{align}

\section{Simulation}

>>>>

\abstract{\todo{abstract}}

@@

\todo{write general introduction to cover times}
"white screen" problem
numerous applications
many mathematical tools

\subsection{Motivation}
\todo{write about applications}
universal travel sequences
graph connectivity
protocol testing
birthday problem
coupon collectors

@@

\todo{outline of each section and subsections}

@@

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\tcov&= \E[X_1+X_2+X_3+\ldots+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
\end{align}

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i)/(n-1)$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (ln-1)(n-i)$.
Then
\begin{align}
\tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
\end{align}

A natural interpretation of the cover time on a complete graph is 
the so-called coupon collecting problem.
There are $r$ different coupons that are randomly packaged in cereal boxes.
An avid fan buys a box of cereal every day.
We want to know how many days until the fan has collected each coupon.
The strategy is to think of every coupon as a vertex on the complete graph.
We then move from vertex to vertex with uniform probability.
The difference between the coupon collecting problem and the complete graph
is that we now have self-edges.
Before, we had to leave our current vertex at each step.
Now, we can stay in the same vertex (provided our collector found the same coupon
two days in a row).
We apply our approach to the complete graph and substitute the $r$ possible coupons
we can find for the $n-1$ vertices we could move to.
Then
\begin{align}
\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+\ldots+1\right). \nonumber
\end{align}

@@

\begin{align}
\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\ldots+1\right). \nonumber
\end{align}

@@

\begin{align}
(e_i - e_1) &= (i-1) e_1 - 2[1+2+\ldots+i-1] \nonumber \\
e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
&= i(N-1 - i + 1) = i(N-i)
\label{eq:line}
\end{align}

@@

We write
\begin{align}
\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \ldots + \E_{i}[T_{i+1}] + \ldots + \E_{N-1}[T_N]. \nonumber
\end{align}

@@

Then
\begin{align}
\E_0[T_N] &= 1 + 3 + \ldots + 2i - 1 + \ldots + 2(N-1) -1 \nonumber \\
&= N^2 \nonumber
\end{align}

@@

\begin{theorem}[Matthews Upper Bound]
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_up}
\end{theorem}
\begin{align}
\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots + \frac{1}{n-1} \right). \nonumber
\end{align}

\begin{proof}
Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
We may assume that the walk started at vertex $n$.
Let $\sigma$ be a uniform permutation of the unvisited $n-1$ vertices.
The strategy is to look for the vertices in order $\sigma$.

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \ldots, \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
$\sigma_1, \sigma_2, \ldots, \sigma_k$ to be visited the first
time they are all visited.

We begin by writing the cover time in a clever way
(similar to the strategy we employed on the cycle graph):
\begin{align}
\tcov &= \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + \ldots + 
(T_k - T_{k-1}) + \ldots + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

Putting it all together,
\begin{align}
\tcov \leq \hit \left( 1+ \frac{1}{2} + \ldots + \frac{1}{k} 
+ \ldots + \frac{1}{n-1} \right). \nonumber
\end{align}
\end{proof}

@@

\begin{theorem}[Matthews Lower Bound]
Let $A \subseteq V(G)$. Define $\tmina = \min_{a,b\in A, a \neq b} \E_b[T_a]$.
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews_low}
\end{theorem}
\begin{align}
\tcov &\geq \tmina \left(1 + \frac{1}{2} + \frac{1}{3} + \ldots +
\frac{1}{|A| -1} \right). \nonumber
\end{align}

\begin{proof}
Without loss of generality, label the vertices $\{1, 2, \ldots, n\}$.
We may assume that the walk started at vertex $x \in A$.
Let $\sigma$ be a uniform permutation of the vertices in $A$.
The strategy is to look for the vertices in order $\sigma$.

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, \ldots, \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$.

We again write the cover time in a clever way:
\begin{align}
\tcov &\geq \E_x[T_1 + (T_2 - T_1) + \ldots + 
(T_k - T_{k-1}) + \ldots + (T_{|A|} - T_{|A|-1})] . \nonumber
\end{align}

@@

Putting it all together,
\begin{align}
\tcov &\geq \tmina \left( 1 - \frac{1}{|A|}+ \frac{1}{2} + \ldots + \frac{1}{k} 
+ \ldots + \frac{1}{|A|-1} + \frac{1}{|A|}\right). \nonumber \\
&= \tmina \left( 1 + \frac{1}{2} + \ldots + \frac{1}{k} 
+ \ldots + \frac{1}{|A|-1} \right). \nonumber
\end{align}
\end{proof}

@@

\cite{LP17}
Consider an unweighted binary tree as in \cref{fig:binary} with a single root $\rho$.
A vertex has two children if it is distance less than $k$
from the root and no children if it is a leaf (distance $k$ from the root).
There are $n = 1 + 2 + 4 + \ldots + 2^k = 2^{k+1} - 1$ vertices.

By \cref{eqn:commute}, the commute time between the root and a leaf $a$ is
\begin{align}
C R_{\rho, a} = 2 (n-1) k \nonumber.
\end{align}
Note that effective resistance adds in series so $\Rxy = i$ where $i$
is the length of the single path between $x$ and $y$.

We first use the Matthews Upper Bound.
The maximum hitting distance is between two vertices whose 
mose recent common ancestor is the root.
For this pair, the hitting time is the same as the commute time
to the root by symmetry.
Consider $a$ and $b$ two leaves whose most recent common ancestor
is the root.
Then
\begin{align}
\E_a [T_b] = \E_a [T_\rho] + \E_\rho [T_a] = 2 (n-1) k \nonumber
\end{align}

and \cref{thm:matthews_up} gives
\begin{align}
\tcov &\leq 2(n-1)k\left(1 + \frac{1}{2} + \ldots + \frac{1}{n} \right) \nonumber \\
&\approx (2 - \frac{2}{n}) \cdot n k \log n \approx (2 - \frac{2}{n}) n k \log 2^{k+1} -1 \nonumber \\
&\approx (2  + o(1)) \cdot n k^2 \log 2 \nonumber
\end{align}

We now use the Matthews Lower Bound.
Choose a set $A \subseteq V(G)$ with a large hitting time between any
pair of vertices.
To find such a set, fix a level $h$ in our binary tree.
Then let $A$ be a set of $2^h$ leaves so that each vertex at level $h$
has a unique descendent in $A$.
As $h$ increases, the distance between the leaves in $A$ decreases.
Thus we want to choose a smaller value of $h$ so that our lower bound will be bigger
(and better).

For $a,b \in A$, the hitting time between $a$ and $b$ is the commute time
from $a$ to their nearest common ancestor at level $h' < h$.
By \cref{eqn:commute}, we have
\begin{align}
\E_a [T_b] = \E_a [T_h'] + \E_{h'} [T_a] = 2 (n-1) (k-h') \nonumber.
\end{align}

In the worst case, $h' = h-1$.
Then by \cref{thm:matthews_low},
\begin{align}
\tcov &\geq 2 (n-1)(k-h+1)\left(1 + \frac{1}{2} + \ldots + \frac{1}{2^h -1} \right) \nonumber \\
&\approx (2 + o(1)) \cdot n (k-h) h \log 2 \nonumber.
\end{align}

If $h=\lfloor k/2 \rfloor$,
\begin{align}
\tcov &\geq \frac{1}{4} ( 2 + o(1) )\cdot nk^2 \log 2\nonumber
\end{align}
then there is a factor of 4 gap between the upper bound and lower bound
of the cover time of a binary tree!

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale = 2]
	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .25pt,-,black!100]
	    \tikzstyle{span}=[draw,line width = 2pt,-,black!100]
	    \node[vertex] (0) at (0,0) {};
	    \node[vertex] (1) at (1,0) {};
	    \node[vertex] (2) at (1,1) {};
	    \node[vertex] (3) at (0,1) {};
	    \draw[span] (0) -- (1);
	    \draw[edge] (0) -- (2);
	    \draw[edge] (0) -- (3);
	    \draw[span] (1) -- (2);
	    \draw[edge] (1) -- (3);
	    \draw[span] (2) -- (3);
	\end{tikzpicture}
	\caption{A spanning tree (in bold) of the complete graph with $n=4$.}\label{fig:span}
\end{figure}

@@

\begin{proof}
Given a spanning tree $\T$, there exists a vertex $v$ with only one edge.
Consider the path $v_0, v_1, \ldots, v_{2n-2}$ where $v=v_0=v_{2n-2}$
that traverses each edge in the spanning once in each direction
and covers every vertex.
We construct this path by starting at $v$ and walking along all $n-1$ edges to the
other vertex with only one edge and then coming back to $v$.

@@

\section{Cover Time Distribution}
\subsection{Complete Graph}
\cite{Du11}
We consider the distribution of the cover time of a random walk
on the complete graph with self edges.
Call $r$ the number of steps since we began the random walk.
So that the notation works out more easily,
set $r=1$ when we begin our walk at $X_0$.
Let $A_i$ be the event that vertex $i$ is not visited and
$N_n$ the number of unvisited vertices.
Then
\begin{align}
P(A_i) = (1-1/n)^r \nonumber
\end{align}
and
\begin{align}
\E[N_n] = n(1-1/n)^r. \nonumber
\end{align}

@@

As $n \rightarrow \infty$,
\begin{align}
\Var(N_n/n) &= \Var(N_n) / n^2 \nonumber\\
&= (1-2/n)^r - (1-1/n)^{2r} + o(n) \nonumber\\
&\rightarrow e^{-2c} - (e^{-c})^2 = 0. \nonumber
\end{align}

@@

We prove the following theorem and then use it to gain insight into
the distribution of the cover time variable $\cov$.
\begin{theorem}\label{thm:pois}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}

@@

By the principle of inclusion-exclusion,
\begin{align}
p_0(r,n) &= {n \choose 0} 1^r - {n \choose 1} (1-1/n)^r + \ldots \nonumber\\
&= \sum_{k=0}^n (-1)^k {n \choose k} (1-k/n)^r. \label{eqn:p0}
\end{align}

@@

Our strategy is to show that $p_m(r,n) \rightarrow \frac{\lambda^m}{m!}e^{-\lambda}$.
The first step is to prove that
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r \rightarrow \lambda ^m /m! \label{eqn:lim}
\end{align}

We bound the expression from the top and the bottom and use the squeeze
theorem to prove the most recent limit.
We will first show the upper bound.
Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
$ne^{r/n} \rightarrow \lambda$.
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} 
= \frac{(n e^{r/n})^m} {m!} \nonumber \\
&\rightarrow \frac{\lambda ^m} {m!}. \nonumber
\end{align}

We now turn to the more tricky lower bound.
Notice that ${n \choose m} \geq (n-m)^m / m!$
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r
&\geq \left(1-\frac{m}{n}\right)^r \frac{(n-m)^m}{m!}
\left( \frac{n^m}{n^m} \right) \nonumber\\
&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  \frac{1}{m!}. \nonumber
\end{align}

As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$
and $1/m!$ is constant.
We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
to bound the rest.
Notice that
\begin{align}
\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \ldots \nonumber\\
&\geq -t -t^2/2(1 + 1/2 + 1/4 + \ldots) = -t - t^2 \nonumber
\end{align}
and so we have
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
& \geq m \log n - r\frac{m}{n} - r\frac{m}{n^2}. \nonumber
\end{align}

We use our assumption that $ne^{r/n} \rightarrow \lambda$
to solve for $r$
\begin{align}
e^{\log n + -r/n} &\rightarrow e^{\log \lambda} \nonumber\\
\log n + -r/n &= \log \lambda + o(n) \nonumber \\
r &= n \log n - n \log \lambda + o(n). \nonumber
\end{align}
Since $r (m/n)^2 \rightarrow 0$ and
\begin{align}
\frac{rm}{n} &=m \log n - m \log \lambda + o(n)\frac{m}{n} \nonumber \\
 m \log n - \frac{rm}{n}&\rightarrow m \log \lambda \nonumber
\end{align}
we have
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&\geq m \log n - \frac{rm}{n} - \frac{rm}{n^2} \rightarrow \log \lambda^m. \nonumber
\end{align}
It follows that
\begin{align}
\lim_{n\rightarrow \infty} n^m\left(1-\frac{m}{n}\right)^r
&\geq \lambda^m. \nonumber
\end{align}

Now we put the pieces back together.
The most recent limit implies \cref{eqn:lim}.
By \cref{eqn:lim} and \cref{eqn:p0},
\begin{align}
p_0(r,n) \rightarrow \sum_{k=0}^\infty \lambda^k /k! = e^{-\lambda}. \nonumber
\end{align}

Notice $p_0(r,n-m)$ also goes to $e^{-\lambda}$
since $m$ is fixed and $(n-m)e^{r/(n-m)} \rightarrow \lambda$.
Finally, the most recent limit and the equation of $p_m(r,n)$ imply
\begin{align}
p_m(r,n) 
&\rightarrow \frac{\lambda^m}{ m!} e^{-\lambda} \nonumber.
\end{align}
$N_n$ approaches a Poisson distribution with mean $\lambda$ as claimed.

@@

We use \cref{thm:pois} to find the distribution of the cover time variable $\cov$.
Set $r = n \log n + nx$.
Then 
\begin{align}
ne^{-r/n} &= n e ^{- \log n - x} \nonumber \\
&= n e {- \log n} e^ {- x} = e^{-x}.\nonumber
\end{align}

Using the fact that $\cov \leq m$ if and only if the first $m$ steps
of the random walk visit all $n$ vertices
and $ne^{-r/n} \rightarrow e^{-x}$ as the assumption of \cref{thm:pois},
\begin{align}
\pr(\cov \leq r) &\rightarrow e^{-e^{-x}} \nonumber \\
\pr(\cov - n \log n\leq nx) &\rightarrow e^{-e^{-x}}. \nonumber
\end{align}

\subsection{Computation}
\todo{example of probability of birthday cover time in x=2190 vs x=1825 steps}

\todo{simulate cover time a thousand times on complete graph with n = 365}
